Approximation as Differentiation: Notes

### 2025-07-04 notes/predicate-system.tex
Ok, natural isomorphism between C \comp -[f] and -[f] \comp C is just the statement that C is a fibred functor.

>>>>

\subsubsection{Closure operator over a predicate system}

A \emph{closure operator} $C$ over a poset $(X, \sqleq)$ is a lax idempotent monad on $X$, with functoriality,
unit and multiplication given by monotonicity, extensivity ($x \sqleq C(x)$) and idempotence ($C(C(x)) \sqleq
C(x)$). Suppose $\mathcal{S} = (\Pred, \top, \meet, \join, \residual, \forall)$ a predicate system over a
category $\cat{C}$. A closure operator $C$ over $\mathcal{S}$ is a fibred lax idempotent monad $C$ on the
fibration $\Pred: \cat{C}^\op \to \Poset$ such that:
\begin{enumerate}
\item for every object $X$ in $\cat{C}$ the fibre map $C_X: \Pred(X) \to \Pred(X)$ is a closure operator;
\item $C$ is fibred, i.e. $C_X \comp \reindex{-}{f}$ is naturally isomorphic to $\reindex{-}{f} \comp C_Y$;
\item $C$ is lax monoidal with respect to $\meet$;
\item $C$ is lax strong, i.e.~$C(X \times Y) \sqleq X \times C(Y)$.
\end{enumerate}
